Transfer learning for echelle spectroscopy

### 2021-11-10 paper/paper1/ms.tex
Start writing prose, now on the Linux machine

At this stage we have a choice of whether to work in linear or log scale units.  Adopting the log of the flux would ensure that the cloned model possesses only positive flux values, a desireable trait of any physical spectral model.  We chose instead to stick with native linear flux scaling because of the availability of convenient approximations to astrophysically relevant line profiles in the linear scaling domain.  We normalize the spectrum by its mean value since we do not intend to apply these methods to absolutely flux calibrated spectra.

@@

We initialize the cloned model with a series of preprocessing steps.  We divide the entire spectrum by a black body of the same temperature as the model template.  This step alone is usually adequate to move on to the spectral line finding.

>>>>

At this stage we have the choice of whether to work in linear or log scale flux units.  Adopting the log of the flux would ensure that the cloned model possesses only positive flux values, a desireable trait of any physical spectral model.  We chose instead to stick with native linear flux scaling because of the availability of convenient approximations to astrophysically relevant line profiles in the linear scaling domain.  We normalize the spectrum by its median value since we do not intend to apply these methods to absolutely flux calibrated spectra.

@@

We initialize the cloned model with a series of preprocessing steps.  We divide the entire spectrum by a black body of the same effective temperature $T_{\mathrm{eff}}$ as the model template.  The resulting signal typically possesses a smooth continuum variation, since
